Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2016-01-21 paper.tex
Define AFT

Chamorro \emph{et al.} \cite{Chamorro2012} showed that turbulence statistics in an AFT%please define
wake became $Re$-independent at $Re_D \approx 1 \times 10^5$ and that mean
velocity profiles became $Re$-independent slightly earlier at $Re_D \approx 5
\times 10^4$. Note that in this study, the tip chord Reynolds number was not
reported, but is estimated to be $Re_c \approx 4 \times 10^4$ at $Re_D=1 \times
10^5$. It is therefore our objective to observe similar scaling relationships
for a cross-flow turbine near-wake.

>>>>

Chamorro \emph{et al.} \cite{Chamorro2012} showed that turbulence statistics in
an horizontal-axis or axial-flow wind turbine wake became $Re$-independent at
$Re_D \approx 1 \times 10^5$ and that mean velocity profiles became
$Re$-independent slightly earlier at $Re_D \approx 5 \times 10^4$. Note that in
this study, the tip chord Reynolds number was not reported, but is estimated to
be $Re_c \approx 4 \times 10^4$ at $Re_D=1 \times 10^5$. It is therefore our
objective to observe similar scaling relationships for a cross-flow turbine
near-wake.
